%-------------------------
% Author: Timothy C. Siwula
%
% File: resume-timothy-siwula.tex
%
% Compile: cd /Users/development/Desktop/projects/professional/resume
%
% pdflatex resume-timothy-siwula.tex && cp resume-timothy-siwula.pdf ~/Desktop open resume-timothy-siwula.pdf
%
%       cd /Users/personal/dev/resume
%
%       pdflatex resume-timothy-siwula.tex
%
%       cp resume-timothy-siwula.pdf ~/Desktop/
%
%       open ~/Desktop/resume-timothy-siwula.pdf
%
%       alias compile_resume="resume && compile_r && move_r && open_r"
%
%       compile_resume
%
%License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{blue}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%  RESUME BEGINS NOW!  %
%-------------------------------------------

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%-------------------------------------------
%  HEADING (TOP LEFT)
%-------------------------------------------
  \textbf{{\Large TIMOTHY C. SIWULA}} \\
  \color{blue}\href{}{https://timsiwula.com} & {+1 (917) 885-3119} \\
  \color{blue}\href{}{https://github.com/timxor/} & \color{blue}{tim@acceptance.ai} \\
  \color{blue}\href{}{https://linkedin.com/in/timsiwula/} & {Chicago, Illinois} \\
\end{tabular*}

%--------TECHNICAL SKILLS------------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \item{
      %--------LANGUAGES------------
      \textbf{Languages}{: Python, Go, C, R, Bash, SQL, Java }
    }
    \item{
      %--------TECHNOLOGIES------------
      \textbf{Technologies}{: Unix/Linux, AWS/Azure/GCP, Docker, Hadoop, PostgreSQL, Git, Terraform, Kubernetes }
    }

    %-------------------------
    % Machine Learning(basic regressing \& classification)
    %-------------------------


    \item{
      %--------FRAMEWORKS------------
      \textbf{Frameworks}{: Node.js, React.js, TensorFlow}
    }
  \resumeSubHeadingListEnd


%----------- EXPERIENCE -----------------
\section{Experience}
  \resumeSubHeadingListStart

  %----------- acceptance ai -----------------
  \resumeSubheading
    {Acceptance AI}{Chicago, IL (Remote)}
    {CEO}{Sept 2019 - Current}
    \resumeItemListStart
      \resumeItem{Government Procurement}
        {Preparing and submiting small business proposals for various federal agencies such as: DARPA, DOE, NSF, Navy and the Air Force.}
        {Writing letter of intents and memorandum of understanding's.}
      \resumeItemListEnd


    %----------- Ensighten -----------------
    \resumeSubheading
      {Ensighten}{Chicago, IL (Remote)}
      {Software Engineer}{Jun 2019 - Oct 2019}
      \resumeItemListStart
        \resumeItem{Dockerized test framework on Bamboo}
          {Worked between teams to port legacy test framework from protractor to cypress within docker.}
        \resumeItem{Data pipeline}
          {Updated Redshift and Hadoop tables in ETL pipeline to support new column for enhanced reporting capability.}
      \resumeItemListEnd

    %-----------ConsenSys-----------------
    \resumeSubheading
      {ConsenSys}{San Francisco, CA (Remote)}
      {Software Engineer}{Jul 2017 - Dec 2018}
      \resumeItemListStart
        \resumeItem{Open-source}
          {Experience in open source development as an individual contributor on Blockchain R\&D, Solidity, Web3, Smart Contracts, functional programming.}
          \resumeItem{Infra}
            {Experience provisioning Azure linux servers for teammates, along with ssh remote access.}
        \resumeItem{Continuous Integration}
          {Configured our teams GitHub repo with Travis CI to ensure the exclusion of failing code while automating passing builds.}
      %  \resumeItem{Tested}
       %   {Worked with the Ethereum Foundation to benchmark new opcodes \& pre-compiles for the Metropolis hard fork.}

        \resumeItem{Shipped}
          {Worked on the Protocol \& Systems Engineering team helping implement Pantheon, an Ethereum enterprise Java client.}
      \resumeItemListEnd

    %-----------HappyChain-----------------
    \resumeSubheading
      {HappyChain}{San Francisco, CA}
      {Co-founder}{Dec 2016 - Jun 2017}
      \resumeItemListStart
        \resumeItem{Deployed}
          {Ethereum blockchain network on AWS, PostgreSQL database, API, solidity smart contracts, web3.}
        \resumeItem{Configured}
          {continuous integration with our GitHub repo to increase deployment speedup.}
        \resumeItem{Published}
          {NPM module that called HappyChain that exposes our API to other developers.}
       \resumeItemListEnd

    %-----------Berkeley Lab-----------------
    \resumeSubheading
      {Lawrence Berkeley National Laboratory}{Berkeley, CA}
      {Science Web Programmer}{May 2014 - Oct 2014}
      \resumeItemListStart
        \resumeItem{System Migration}
          {Ported the Energy Sciences network testbed to a new architecture. This consisted of a linux OS and a network file system.}
        \resumeItem{Reservation System}
          {Developed a front-end web application using javascript on google cloud.}
       \resumeItemListEnd

    %-----------USF-----------------
    \resumeSubheading
      {University of San Francisco}{San Francisco, CA}
      {Research Assistant}{Spring 2014 and Spring 2017}
      \resumeItemListStart
        \resumeItem{Compilers}
          {Contributed to an open source MIT project called App Inventor. Worked on a javascript to java translator and code generator.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{HappyENS}
      {Open source domain name server (DNS) library for resolving *.eth domains that are associated to an address on the decentralized web.}
  \resumeSubItem{Ad Click Prediction}
      {Used random forests, bagging and SVM to create a model that predicts the likelihood of a user clicking through. Created custom features by integrating several disjoint tables in increments of 500K using R and Postgres.}
  \resumeSubItem{The Comedy Bot}
      {Published: Messenger chatbot that was live in production on Facebook \& Deployed: Heroku node server that calls AWS lambda for requests \& Twilio sms chatbot.}
  \resumeSubHeadingListEnd

  %----------- EDUCATION -----------------
  \section{Education}
    \resumeSubHeadingListStart
      \resumeSubheading
        {University of San Francisco}{San Francisco, CA}
        {Bachelor of Science in Computer Science}{Jan. 2014 -- May. 2017}
    \resumeSubHeadingListEnd

    %-----------Technical Achievements (hackathons, publications or patents-----------------
    \section{Technical Achievements}
      \resumeSubHeadingListStart

        \resumeSubItem{2017 - Winning team}
            {ETH Waterloo Hackathon, Waterloo, Canada.}

        \resumeSubItem{2017 - Published}
            {HappyChain API SDK via node package module.}

        \resumeSubItem{2014 - Participant}
            {Salesforce Hackathon, San Francisco, CA.}

        \resumeSubItem{2014 - Participant}
            {ACM International Collegiate Programming Contest, San Francisco, CA.}

      \resumeSubHeadingListEnd


    %-----------Leadership Activities-----------------
    \section{Leadership Activities}
      \resumeSubHeadingListStart

      % ussocom - sme
       \resumeSubItem{2020 - Subject Matter Expert}
          {Innovation Foundry Artificial Intelligence, United States Special Operations Command, Remote.}

        % hack in the north - judge
         \resumeSubItem{2018 - Hackathon Judge}
            {Hack in the North, IIIT-Allahabad, India.}

        % wcef - judge
        \resumeSubItem{2018 - Hackathon Judge}
            {World Crypto Economic Forum (WCEF), San Francisco, CA}

        % incubator mentor - d.c.
        \resumeSubItem{2018 - Hackathon Mentor}
            {Decentralized Impact Incubator 6-week Hackathon, Washington, D.C. \& Remote.}

        % hackathon mentor - dubai
        \resumeSubItem{2017 - Hackathon Mentor}
            {ConsenSys Academy Hackathon, Dubai, United Arab Emirates.}

        % usf ra
        \resumeSubItem{2014 - President}
            {Resident Hall Council, University of San Francisco.}

        % volunteer
        \resumeSubItem{2013 - Volunteer}
            {Habitat for Humanity.}

        % occ as
        \resumeSubItem{2010 - Director of Publicity}
            {Associated Students, Orange Coast College.}

      \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
